Submission HW1

### 2022-08-31 hw1-1/submission.Rmd
Final code submission

-   ***Current Debt to Income ratio***: This is a measure of Income to Debt Capacity of the individual. In other words, it stacks up the overall debt obligations of the individual across mortgage, auto loan, credit cards etc., against his total income. If a larger part of an individual's income is directed towards his debt payment, than he/she again might be more susceptible to miss payments in the future and hence is riskier.

@@

**Objective Function (**$Y$): To classify whether a readmission will happen within 30 days of the Inpatient discharge for a given patient.\
**Predictor Variables (**$X_i$): Some of the key predictor variables given below:

@@

```{r}
#lib imports
library(cowplot)
library(ggplot2)
library(reshape2)
library(kknn)
library(pROC)
```

@@

-   C=0.001: While here the overall accuracy drops to 83% but accuracy in the negative class is significantly higher at 92%, and given this is a loan application example, it might be better to gear the model more towards the negative class.

@@

As expected (from distribution plots) variables A9, A11, A8, A10 show very significant weights in the decision boundary. Similarly variables like A1,A2 have very low weights, and can also be dropped.

@@

As seen for Linear Kernels, increase in C, increases accuracy while decreasing number of support vectors. Because this is a very complex model, we are able to get very high accuracy, however we can't be sure if the same would generalize to unseen data.

@@

Here again we are able to get 100 accuracy, however we can't be sure if the same would generalize to unseen data.

@@

We implement vanilla knn model here, with rectangular kernel and majority voting (i.e probability threshold \>0.5) among neighbors to decide predicted label.

@@

The graph above here plots Accuracy on y-axis vs 'k'. As we increase the k, Accuracy is mostly static and after a certain threshold, it starts dropping almost linearly to 55%, where it then stabilizes. The 55% number here is intuitive since with as many nearest neighbors as the #data points, the prediction decision basically boils down to assigning the majority label in the dataset, i.e. Negative. Therefore, for 55% the negative class, we receive a correct prediction while the rest 45% Positive class is misclassified.

### Optimisation over 'k' and probability threshold

@@

```{r}
# Final step to determine the highest value of AUC for every K
final_frame<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))
for(k_i in seq(20, 50, by=5)){
  print(k_i)
  data_i = threshold_auc[threshold_auc$k == k_i,]
  print (data_i[which.max(data_i$auc_val),])
  final_frame[nrow(final_frame)+1, ] <- data_i[which.max(data_i$auc_val),]
}
```

@@

>>>>

-   ***Current Debt to Income ratio***: This is a measure of Debt to Income Capacity of the individual. In other words, it stacks up the overall debt obligations of the individual across mortgage, auto loan, credit cards etc., against his total income. If a larger part of an individual's income is directed towards his debt payment, than he/she again might be more susceptible to miss payments in the future and hence is riskier.

@@

**Objective Function (**$Y$): To classify whether a readmission will happen within 30 days of the Inpatient (Hospital) discharge for a given patient.\
**Predictor Variables (**$X_i$): Some of the key predictor variables given below:

@@

```{r, include=FALSE}
#lib imports
library(cowplot)
library(ggplot2)
library(reshape2)
library(kknn)
library(pROC)
```

@@

-   C=0.001: While here the overall accuracy drops to 83% but accuracy in the negative class is significantly higher at 92%, and given this is a loan application example, it might be better to gear the model more towards the negative class. This is because it might be more riskier to approve the loan application for a person who ought to be denied the loan application versus misclassifying an otherwise approved applicant.

@@

**As expected (from distribution plots) variables A9, A11, A8, A10 show very significant weights in the decision boundary. Similarly variables like A1,A2 have very low weights, and can also be dropped.**

@@

As seen for Linear Kernels, increase in C, increases accuracy while decreasing number of support vectors. Because this is a very complex model, we are able to get very high accuracy on the training data, however we can't be sure if the same would generalize to unseen data.

@@

Here again we are able to get 100 accuracy (it appears as if it is grossly overfitting), hence we can't be sure if the same performance would generalize to unseen data.

@@

We implement vanilla knn model here, with rectangular (standard unweighted) kernel and majority voting (i.e probability threshold \>0.5) among neighbors to decide predicted label.

@@

The plot above shows the Accuracy on y-axis vs 'k' i.e number of nearest neighbours on the x-axis. As we increase k, Accuracy is mostly static and after a certain threshold (~340), it starts dropping almost linearly to 55%, where it then stabilizes. The 55% number here is intuitive since with as many nearest neighbors as the #data points, the prediction decision basically boils down to assigning the majority label in the dataset, i.e. Negative.

**At this point, we receive a correct prediction on the negative class which constitute around 55% of the overall number of data points, while the rest 45% Positive class is misclassified.**

### Optimisation over 'k' and probability threshold
The KNN model as compared to SVM model provides us the prediction probability of each point being in a given class which can then be transformed into predicted labels based on the threshold value.
This introduces the notion of deciding an optimal threshold value that maximizes our chosen metric. A typically used metric for classification problem is the AUC value under the ROC curve.

https://en.wikipedia.org/wiki/Receiver_operating_characteristic

In the code below , we have employed an approach of iterating over k and finding an optimal probability threshold corresponding to each k which maximizes the AUC score.

@@

```{r}
# Final step to determine the highest value of AUC for every K
final_frame<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))
for(k_i in seq(20, 50, by=5)){
  #print(paste("Best Probability threshold for k=",k_i))
  data_i = threshold_auc[threshold_auc$k == k_i,]
  #print (data_i[which.max(data_i$auc_val),])
  final_frame[nrow(final_frame)+1, ] <- data_i[which.max(data_i$auc_val),]
}
```

@@

[**#Analysis:**]{style="color:red"}
From above table we are able to choose a combination of k and threshold values, so as to maximize accuracy.
However, the combinations listed above exhibit very similar Accuracy ranges (overall and split by classes as well.)
